---
title: "Meal Plan Report"
output: html_document
params:
  user_name: "Unknown"
  report_date: !r Sys.Date()
  targets: NULL
  pct_to_plan: 1.0
  slots: NULL
  meal_details: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(knitr)
library(kableExtra)
```

<style>
  /* Tip is only useful on screen */
  .print-tip {
    background: #eef6ff;
    border-left: 4px solid #4a90e2;
    padding: 0.5em 0.9em;
    margin: 0 0 1em 0;
    font-size: 0.9em;
    color: #333;
  }
  @media print {
    .print-tip { display: none; }
    body { font-size: 11pt; }
    h1 { page-break-before: auto; }
    h3 { page-break-after: avoid; }
    table { page-break-inside: avoid; }
    a { color: inherit; text-decoration: none; }
  }
</style>

<div class="print-tip">
  <strong>Tip:</strong> to save this report as a PDF, press
  <kbd>Ctrl</kbd>+<kbd>P</kbd> (or <kbd>⌘</kbd>+<kbd>P</kbd> on Mac) and
  choose <em>Save as PDF</em> as the destination.
</div>

# Meal Plan — `r params$user_name`
**Date:** `r format(params$report_date, "%d %B %Y")`

---

## 1. Daily Summary & Targets

```{r summary}
kable(params$targets, format = "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

---

## 2. Plan

```{r plan}
kable(params$slots, format = "html",
      col.names = c("Slot Name", "Meal", "Servings")) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE)
```

---

## 3. Meals

```{r meals, results='asis'}
for (i in seq_along(params$meal_details)) {
  meal <- params$meal_details[[i]]

  if (isTRUE(meal$is_additional)) {
    cat("\n\n### Additional Ingredients\n\n")
  } else {
    cat(paste0("\n\n### Slot ", i, " — ", meal$slot_name, ": ", meal$meal_name,
               " (", meal$servings, " serving(s))\n\n"))
  }
  
  tbl <- kable(meal$ingredients, format = "html",
        col.names = c("Ingredient", "Portions", "Calories", 
                      "Protein (g)", "Carbs (g)", "Fat (g)")) %>%
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                    full_width = FALSE) %>%
      row_spec(nrow(meal$ingredients), bold = TRUE, background = "#f5f5f5")
  
  cat(as.character(tbl))
  cat("\n\n")
}
```